ms_8

### 2020-04-24 ms_8.Rmd
finished plotting data for food_access

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
```

@@

```{r obesity mean plot, include=FALSE}

@@

```{r obesity by region}

@@

obesity_region_plot <- obesity_region %>% 
    filter(!is.na(region)) %>%
    ggplot(aes(color = region, x = year, y = mean_perc)) +
    geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
    theme_minimal() +
    labs(title = "Percent of Population Classified as Obese or Overweight \n in US Over Time by Region",
         caption = "Data from Center for Disease Control",
         x = "Mean Percent of Population",
         y = "Year",
         color = "Region") +
    geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
    facet_wrap(~ region)
obesity_region_plot

@@

food_access <- food_access_x %>% 
    rename("state" = State,
           "county" = County,
           "popul" = POP2010,
           "urban" = Urban,
           "lia_1_10" = LILATracts_1And10,
           "poverty_rate" = PovertyRate,
           "med_income" = MedianFamilyIncome,
           "la_1_10" = LA1and10,
           "la_popul" = LAPOP1_10) %>% 
    mutate(urban = as.factor(urban),
           lia_1_10 = as.factor(lia_1_10),
           la_1_10 = as.factor(la_1_10))

food_access$state = state.abb[match(food_access$state, state.name)]

View(food_access)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
library(scales)
```

@@

```{r obesity mean by year, include=FALSE}

@@

```{r obesity by region, include=FALSE}

@@

obesity_region_plot <- obesity_region %>% 
    filter(!is.na(region)) %>%
    ggplot(aes(color = region, x = year, y = mean_perc)) +
    geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
    theme_minimal() +
    labs(title = "Percent of Population Classified as Obese or Overweight \n in US Over Time by Region",
         caption = "Data from Center for Disease Control",
         x = "Mean Percent of Population",
         y = "Year",
         color = "Region") +
    geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
    facet_wrap(~ region)

obesity_region_plot

@@

food_access_y <- food_access_x %>% 
    rename("state" = State,
           "county" = County,
           "popul" = POP2010,
           "urban" = Urban,
           "lia_1_10" = LILATracts_1And10,
           "poverty" = PovertyRate,
           "med_income" = MedianFamilyIncome,
           "la_1_10" = LA1and10,
           "la_popul" = LAPOP1_10) %>% 
    mutate(urban = as.factor(urban),
           lia_1_10 = as.factor(lia_1_10),
           la_1_10 = as.factor(la_1_10))

food_access_y$state = state.abb[match(food_access_y$state, state.name)]

food_access <- food_access_y %>% 
    mutate(region = case_when(
        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
                     "LA", "OK", "TX") ~ "South",
        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West")
    ) %>% 
    select(-county)

```{r mean poverty by state, include = FALSE}

food_poverty_mean <- food_access %>%
    filter(!is.na(region)) %>% 
    group_by(state) %>% 
    summarise(mean_poverty = mean(poverty))

food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
                                     color = "green", labels = FALSE) +
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "green", name = "Mean Poverty Rate") +
    labs(title = "Poverty Rate in the US",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
    theme_void()
food_poverty_mean_plot

ggsave("plots/food_poverty_plot.png", plot = last_plot())

```{r food access lia distribution, include=FALSE}

food_lia <- food_access %>%
    filter(!is.na(region)) %>% 
    group_by(state, region) %>% 
    summarise(perc = sum(lia_1_10 == 1)/n()) %>% 
    mutate(perc = perc*100) %>% 
    mutate(perc = round(as.numeric(perc), digits = 0)) %>% 
    arrange(perc)

# food_lia$perc =  paste(round(100*food_lia$perc, digits = 0), "%", sep="")

food_lia_plot <- food_lia %>% 
    group_by(region) %>% 
    ggplot(aes(x = reorder(state, perc), y = perc, fill = region)) +
    geom_col() +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 65, hjust = 0.3, size = 7),
          panel.grid.major.x = element_line(color = "white"),
          plot.subtitle = element_text(size = 8)) +
    labs(title = "Percent of Counties with a Lack of Food Access",
         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store",
         caption = "Data from US Department of Agriculture and 2010 Census Bureau",
         x = "State",
         y = "Percent of Counties",
         fill = "Region")

food_lia_plot

ggsave("plots/food_lia_plot.png", plot = last_plot())
